Modeling and Simulation of Load Balancing Strategies for Computing in High Energy Physics

### 2018-10-09 paper/paper.tex
Remove scheduling delay

After a job is scheduled on a resource container, it acquires the specified number of job slots or waits if the node has not sufficient free slots. Afterwards, the CPU and I/O demands of the job are processed. To avoid one big I/O operation at the start of a job and to make the processing of I/O more continuously, the processing is modeled using iterations that reflect the number of events. Thus, for each iteration there are I/O and CPU resources needed. Rather than simulating each event, we simulate a fraction of the processed events, because the simulation of each event would harm the scalability of the simulation. 
While processing, the job uses the specified number of cores to process the CPU demand. To simulate not explicitly modeled elements of the jobs such as the overhead created by pilot jobs we added a delay to each job. This delay is calibrated in order to match the measured throughput of the test data. After the job finished, it releases its acquired job slots. All of these parameters are specified as a probability function and are extracted from measured performance data as described in \Cref{sec:param}.

@@

As mentioned in \Cref{sec:model} a delay was added to the job to simulate the effects of not explicitly modeled elements. This delay was calibrated so that the measured throughput matches the simulated one of the calibration dataset. The simulated throughput of the test dataset matches the measured one accurately with only 1\% difference.
\Cref{shares} depicts the share of the simulated and measured job types, which also have a high accuracy.

>>>>

After a job is scheduled on a resource container, it acquires the specified number of job slots or waits if the node has not sufficient free slots. Afterwards, the CPU and I/O demands of the job are processed. To avoid one big I/O operation at the start of a job and to make the processing of I/O more continuously, the processing is modeled using iterations that reflect the number of events. Thus, for each iteration there are I/O and CPU resources needed. Rather than simulating each event, we simulate a fraction of the processed events, because the simulation of each event would harm the scalability of the simulation. 
While processing, the job uses the specified number of cores to process the CPU demand. After the job finished, it releases its acquired job slots. All of these parameters are specified as a probability function and are extracted from measured performance data as described in \Cref{sec:param}.

@@

The simulated throughput of the test dataset matches the measured one accurately with only 1\% difference.
\Cref{shares} depicts the share of the simulated and measured job types that also shows  a high accuracy.
